Multi-modality Imagery Database for Plant Phenotyping

### 2015-05-01 datapaper_baseline.tex
xm's first edits

\subsection{Performance and analysis}
We apply our algorithm on all $144$ frames of each video and evaluate the performance on labeled $36$ frames.
Leaf alignment is applied to the last frame of each video. 
Figure~\ref{fig:alignResult} shows some examples of leaf alignment results. 
Our framework works very well on segmenting large leaves with no overlap to neighbor leaves. 
For overlapping leaves, it becomes more challenging as the edges between the overlapping area are more difficult to be detected. 
However, when the overlapping leaves are further away from the center, they will have a higher chance to be detected as shown in $(3)$ of Fig.~\ref{fig:alignResult}. 
When the overlapping leaves are close to the center, smaller leaves will be covered by larger leaves as shown in $(1), (4), (5)$ of Fig.~\ref{fig:alignResult}.

Leaf alignment provides the leaf candidates for tracking over time. 
One example of leaf tracking result is shown in Fig.~\ref{fig:trackExample}. 
The leaf template transformation works well for most leaves. 
As plant grows, younger leaves may grow faster than older leaves and occlude the older leaves. 
Our backward tracking algorithm tracks leaves from last frame to first frame. 
Leaves will be deleted when it becomes small and the leaf underneath it will be detected. 
As shown in Fig,~\ref{}, leaf $X$ replace leaf $X$ at day $X$, which is considered as a tracking failure.

@@

For quantitative evaluation, we vary $\tau$ from 0 to 1 and generate the first three evaluation metrics, as shown in Fig.~\ref{fig:performance}.
{\it{ULR}} decreases as $\tau$ increases as more leaves are being considered as matched leaves.  
As $\tau$ keep increasing, {\it{ULR}} approaches a constant value, which is the the diferent number in leaf counting that results from both miss detection and false alarms. 
{\it{LE}} increases as $\tau$ increases as it includes leaves with larger tip-based errors for averaging. 
{\it{TC}} increases as $\tau$ increases as more leaves are being considered as correctly tracked leaves. 
Overall, our method can detect $80\%$ and track $60\%$ of all labeled leaves with $XX$ average tip-based errors.

>>>>

\subsection{Performance and analysis}
We apply our algorithm on all $144$ frames of each video and evaluate the performance on labeled $36$ frames.
Leaf alignment is applied to the last frame of each video. 
Figure~\ref{fig:alignResult} shows some examples of leaf alignment results. 
Our framework works very well on segmenting large leaves with no overlap to neighbor leaves. 
For overlapping leaves, it becomes more challenging as the edges between the overlapping area are more difficult to be detected. 
However, when the overlapping leaves are further away from the center, they will have a higher chance to be detected as shown in $(3)$ of Figure~\ref{fig:alignResult}. 
When the overlapping leaves are close to the center, smaller leaves will be covered by larger leaves as shown in $(1), (4), (5)$ of Figure~\ref{fig:alignResult}.

Leaf alignment provides the leaf candidates for tracking over time. 
One example of leaf tracking result is shown in Figure~\ref{fig:trackExample}. 
The leaf template transformation works well for most leaves. 
As plant grows, younger leaves may grow faster than older leaves and occlude the older leaves. 
Our backward tracking algorithm tracks leaves from last frame to first frame. 
Leaves will be deleted when it becomes small and the leaf underneath it will be detected. 
As shown in Figure~\ref{}, leaf $X$ replace leaf $X$ at day $X$, which is considered as a tracking failure.

@@

For quantitative evaluation, we vary $\tau$ from $0$ to $1$ and generate the first three evaluation metrics, as shown in Figure~\ref{fig:performance}.
{\it{ULR}} decreases as $\tau$ increases as more leaves are being considered as matched leaves.  
As $\tau$ keep increasing, {\it{ULR}} approaches a constant value, which is the the diferent number in leaf counting that results from both miss detection and false alarms. 
{\it{LE}} increases as $\tau$ increases as it includes leaves with larger tip-based errors for averaging. 
{\it{TC}} increases as $\tau$ increases as more leaves are being considered as correctly tracked leaves. 
Overall, our method can detect $80\%$ and track $60\%$ of all labeled leaves with $XX$ average tip-based errors.

### 2015-05-01 datapaper_calibration.tex
xm's first edits

A planar checkerboard pattern was used to calibrate all three cameras to obtain both intrinsic and extrinsic parameters.  While the grid pattern is not visible in the depth image, it is nevertheless observed in the reflected IR image whose pixels correspond to the depth pixels.  This enables the use of Zhang's method~\cite{Zhang2000} to calculate the intrinsic parameters including a $2$-parameter radial distortion of each camera.  In this process the poses of all three cameras are also calculated relative to the checkerboard.  The intrinsic and extrinsic parameters are stored as text files, and a Matlab function is provided that reads the parameters and can plot the camera poses as in Fig.~\ref{fig:CameraConfiguration}.

@@

The depth noise $\epsilon$ is modeled as the sum of two components, $\epsilon_I$ and $\epsilon_S$: 
\begin{equation}
	\epsilon = \epsilon_I + \epsilon_S\label{eq:epsilon}
\end{equation}
The term $\epsilon_I$ captures the noise component that varies between images taken from a fixed pose of a static scene. On the other hand the term $\epsilon_S$ models noise that is constant between images but varies between pixels. The variance of $\epsilon_I$ can be estimated by observing pixels of a fixed scene over multiple images.  In our experiments we observed a flat, uniform albedo surface perpendicular to the camera at a sequence of depths, and for each depth acquiring 300 images.  Object depth has a large impact on $\epsilon_I$ likely due to reduced reflected signal.  For constant depth, we observed that the primary factor affecting the variance is the pixel radius from the image center.  Physically we expect this dependence is due to a circularly symmetric illuminating beam closely aligned with the optical axis.  Based on these observations $\sigma_I^2$, the variance of $\epsilon_I$, is empirically estimated as a function of object depth and pixel radius as shown in Fig.~\ref{fig:Noise}.

>>>>

A planar checkerboard pattern was used to calibrate all three cameras to obtain both intrinsic and extrinsic parameters.  While the grid pattern is not visible in the depth image, it is nevertheless observed in the reflected IR image whose pixels correspond to the depth pixels.  This enables the use of Zhang's method~\cite{Zhang2000} to calculate the intrinsic parameters including a $2$-parameter radial distortion of each camera.  In this process the poses of all three cameras are also calculated relative to the checkerboard.  The intrinsic and extrinsic parameters are stored as text files, and a Matlab function is provided that reads the parameters and can plot the camera poses as in Figure~\ref{fig:CameraConfiguration}.

@@

The depth noise $\epsilon$ is modeled as the sum of two components, $\epsilon_I$ and $\epsilon_S$: 
\begin{equation}
	\epsilon = \epsilon_I + \epsilon_S\label{eq:epsilon}
\end{equation}
The term $\epsilon_I$ captures the noise component that varies between images taken from a fixed pose of a static scene. On the other hand the term $\epsilon_S$ models noise that is constant between images but varies between pixels. The variance of $\epsilon_I$ can be estimated by observing pixels of a fixed scene over multiple images.  In our experiments we observed a flat, uniform albedo surface perpendicular to the camera at a sequence of depths, and for each depth acquiring 300 images.  Object depth has a large impact on $\epsilon_I$ likely due to reduced reflected signal.  For constant depth, we observed that the primary factor affecting the variance is the pixel radius from the image center.  Physically we expect this dependence is due to a circularly symmetric illuminating beam closely aligned with the optical axis.  Based on these observations $\sigma_I^2$, the variance of $\epsilon_I$, is empirically estimated as a function of object depth and pixel radius as shown in Figure~\ref{fig:Noise}.

### 2015-05-01 datapaper_intro.tex
performance
xm's first edits

@@

To facilitate future research on plant image analysis, as well as remedy the limitation of existing databases in the field, this paper presents a newly collected multi-modality plant imagery database through an interdisciplinary effort at Michigan State University (MSU), termed ``MSU-PID''. 
The MSU-PID database includes the imagery of two types of plants (Arabidopsis and bean), both are widely used in plant research, captured by four types of imaging sensors, i.e., Fluorescence, infrared (IR), RGB color, and depth.
All four sensors are synchronized and are programmed to periodically capture imagery data for multiple consecutive days. 
Checkerboard-based camera calibration is performed between a pair of sensors, which results in the explicit correspondence between the pixels of {\it any} two modalities.

>>>>

\begin{figure*}
\begin{centering}
\begin{tabular}{@{}c c c c}
%\begin{tabular}{lllllllll}
\includegraphics[width=.23\textwidth]{Figures/FourModalities/A_rgb}&
\includegraphics[width=.23\textwidth]{Figures/FourModalities/A_depth}&
\includegraphics[width=.23\textwidth]{Figures/FourModalities/A_fmp}&
\includegraphics[width=.23\textwidth]{Figures/FourModalities/A_ir}\\
Arabidopsis: RGB &  Arabidopsis: Depth & Arabidopsis: Fluorescence & Arabidopsis: IR \\
\includegraphics[width=.23\textwidth]{Figures/FourModalities/B_rgb}&
\includegraphics[width=.23\textwidth]{Figures/FourModalities/B_depth}&
\includegraphics[width=.23\textwidth]{Figures/FourModalities/B_fmp}&
\includegraphics[width=.23\textwidth]{Figures/FourModalities/B_ir}\\
Bean: RGB &  Bean: Depth & Bean: Fluorescence & Bean: IR \\
\end{tabular}
\caption{The multi-modality plant imagery database of MSU-PID. }
\label{fig:fourmodality}
\end{centering}
\end{figure*}

@@

To facilitate future research on plant image analysis, as well as remedy the limitation of existing databases in the field, this paper presents a newly collected multi-modality plant imagery database through an interdisciplinary effort at Michigan State University (MSU), termed ``MSU-PID''.
As illustrated in Figure~\ref{fig:fourmodality}, the MSU-PID database includes the imagery of two types of plants (Arabidopsis and bean), both are widely used in plant research, captured by four types of imaging sensors, i.e., Fluorescence, infrared (IR), RGB color, and depth.
All four sensors are synchronized and are programmed to periodically capture imagery data for multiple consecutive days.
Checkerboard-based camera calibration is performed between a pair of sensors, which results in the explicit correspondence between the pixels of {\it any} two modalities.
